An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-30 paper/1.introduction.tex
minor

Both methods were fully implemented for minBiGUL, a core bidirectional language. The experimental results show that our methods are much faster than the original evaluation strategy.
Iwe give detailed experimental results in Section~\ref{sect:experiments}, discuss related work in Section~\ref{sect:related}, and conclude in Section~\ref{sect:conclusion}.

>>>>

Both methods have been fully implemented for minBiGUL, a core bidirectional language. The experimental results show that our methods are much faster than the original evaluation strategy.
We give detailed experimental results in Section~\ref{sect:experiments}, discuss related work in Section~\ref{sect:related}, and conclude in Section~\ref{sect:conclusion}.
